Msc Thesis Figures

### 2020-07-20 Rmd/msc_thesis_figures.Rmd
fixes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = normalizePath(".."))
suppressPackageStartupMessages({
  library(raster)
  library(sf)
  library(tidyverse)
  library(ggplot2)
  library(gganimate)
  library(transformr)
  library(animation)
  library(rasterVis)
  library(ggmap)
  library(gifski)
  library(gtools)
  library(fmsb)
  library(RColorBrewer)
  library(scales)
  library(ggradar)
  library(tidymodels)
  library(patchwork)
})
```

@@

@@

# Histogram data 
histograms <- read_csv("outputs/final/final_values_output.csv") %>% 
  left_join(results_clean, by="sce")

@@

#### Set the ggplot theme

We see the ggplot theme to `theme_minimal()` and change the size of some plot elements.

```{r set_ggplot_theme}
theme_set(theme_minimal())
theme_update(legend.position = c(0.85, 0.20),
             legend.box = "vertical",
             legend.background = element_blank(),
             legend.box.background = element_rect(colour = "black"),
             panel.border = element_rect(fill = NA),
             legend.title = element_text(size = 15),
             legend.text = element_text(size = 13),
             plot.title = element_text(size=20),
             plot.subtitle = element_text(size=20),
             axis.text.x = element_text(angle=65, vjust=0.6, size =13),
             axis.text.y = element_text(size =13),
             strip.text.x = element_text(size = 13),
             strip.text.y = element_text(13),
             axis.title=element_text(size=18))
```

@@

```{r fig_1_historic, message=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 1990-2010"}
fig_1_historic <- joined %>% 
  filter(climate == "none") %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 1990)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=source)) +
  scale_color_manual(values=c('#d8b365','#5ab4ac'), 
                     labels = c("Model", "Observation")) +
  geom_smooth(aes(group = sce), method = "glm", se=FALSE) +
  scale_linetype_manual(values = c(1,3,2,5))+
  geom_point(aes(group = sce)) +
  facet_wrap(~species, scales = "fixed") +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Source") +
  NULL
fig_1_historic
ggsave(fig_1_historic,
       filename = "outputs/figures/connectivity_decrease_x5species_historic.png",
       width = 15, height = 15, dpi = 500)
```
#### Chap 1

@@

```{r figure_1_model_1, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100", message=FALSE}
fig_1_static_chap_1 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  #geom_point(aes(group = sce)) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  #geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
fig_1_static_chap_1
ggsave(fig_1_static_chap_1, 
       filename = "outputs/figures/connectivity_decrease_x5species_chap1.png", 
       width = 15, height = 15)
```

@@

radar_chap1 <-  
  ggradar(radar_data_chap1, centre.y = -20, legend.position = "right",
          grid.min = -20, grid.max = 3, grid.mid = 0, 
          values.radar = c("-20 %", "0 %", ""), 
          gridline.label.offset	=5, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
radar_chap1
ggsave("outputs/figures/radar_ggradar_chap1.png", radar_chap1, width = 15, height = 10)
```

@@

```{r figure_1_model_2, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100", message=FALSE}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
fig_1_static_chap_2
ggsave(fig_1_static_chap_2, 
       filename = "outputs/figures/connectivity_decrease_x5species_chap2.png", 
       width = 15, height = 15)
```
##### Radar Graph

@@

radar_chap2 <-  
  ggradar(radar_data_chap2, centre.y = -20, legend.position = "right",
          grid.min = -20, grid.max = 3, grid.mid = 0, 
          values.radar = c("-20 %", "0 %", ""), 
          gridline.label.offset	=5, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
radar_chap2
ggsave("outputs/figures/radar_ggradar_chap2.png", radar_chap2, width = 15, height = 10)
```

@@

radar_all <-  
  ggradar(radar_data_all, centre.y = -20, legend.position = "right",
          grid.min = -20, grid.max = 3, grid.mid = 0, 
          values.radar = c("-20 %", "0 %", ""), 
          gridline.label.offset	=5, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
radar_all
ggsave("outputs/figures/radar_ggradar_both.png", radar_all, width = 15, height = 10)
```

@@

```{r figure_2_chap1, eval=FALSE, message=FALSE, warning=FALSE}
# change_1 <- df_final_fordiff_pivoted %>% 
#   filter(chapter %in% c("none", "both", "chap_1")) %>%
#   filter(sce %in% c('sce_38', 'sce_39')) %>% 
#   ggplot(aes(fill=change)) +
#   geom_sf(show.legend=T, lwd = 0)  + 
#   facet_wrap(~sce) + 
#   ggtitle("Connectivity change in %", 
#           subtitle = "2010-2100") +
#   scale_fill_binned(low='#d13e11', high='#fff7bc', 
#                     breaks=c(-50, -40, -30, -20, -10, 0, 10))
# change_1
#ggsave("outputs/figures/connectivit_change_mun_chap1.png", change_1)
```

@@

```{r figure_2_chap2, eval=FALSE, message=FALSE, warning=FALSE}
# change_2 <- df_final_fordiff_pivoted %>% 
#   filter(chapter %in% c("none", "both", "chap_2")) %>%
#   ggplot(aes(fill=change)) +
#   geom_sf(show.legend=T, lwd = 0)  + 
#   facet_wrap(~sce) + 
#   ggtitle("Connectivity change in %", 
#           subtitle = "2010-2100") +
#   scale_fill_binned(low='#d13e11', high='#fff7bc', 
#                     breaks=c(-50, -40, -30, -20, -10, 0, 10))
# change_2
#ggsave("outputs/figures/connectivit_change_mun_chap2.png", change_2)
```

@@

```{r figure_2_all, eval=FALSE, message=FALSE, warning=FALSE}
# change_both <- df_final_fordiff_pivoted %>% 
#   ggplot(aes(fill=change)) +
#   geom_sf(show.legend=T, lwd = 0)  + 
#   facet_wrap(~sce) + 
#   ggtitle("Connectivity change in %", 
#           subtitle = "2010-2100") +
#   scale_fill_binned(low='#d13e11', high='#fff7bc', 
#                     breaks=c(-50, -40, -30, -20, -10, 0, 10))
# change_both
#ggsave("outputs/figures/connectivit_change_mun_both.png", change_both)
```

@@

```{r roc_curves, message=FALSE, warning=FALSE, out.width="100%"}
p1 <- bind_rows(urb, .id = "fold") %>% 
  mutate(Fold = factor(fold, levels = as.character(1:10))) %>% 
  group_by(Fold) %>% 
  roc_curve(.pred, truth = outcome_fact) %>% 
  autoplot(add=T) +
  ggtitle(paste("Urbanisation")) +
  annotate(x = 0.75, y = 0.25, geom="label", 
           label = as.character(paste("Av AUC = 0.938 +/- 0.002"))) +
  theme(legend.position = "none") +
  NULL

p2 <- bind_rows(agex, .id = "fold") %>% 
  mutate(Fold = factor(fold, levels = as.character(1:10))) %>% 
  group_by(Fold) %>% 
  roc_curve(.pred, truth = outcome_fact) %>% 
  autoplot(add=T) +
  ggtitle(paste("Agricultural Expansion")) +
  annotate(x = 0.75, y = 0.25, geom="label", 
           label = as.character(paste("Av AUC = 0.929 +/- 0.002"))) +
  NULL

@@

full
ggsave("outputs/figures/double_roc_resample.png", full)
```

@@

```{r hist_plot_1, out.width="100%"}
hist_plot_1 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('both', 'chap_1')) %>%  
  ggplot(aes(x=bins, y=n, group=ts, colour=ts)) + 
  geom_density(stat='identity', show.legend=F, aes(fill=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  labs(x = "Flow intensity distribution (log)", 
       y = "")+
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank()) +
  NULL
hist_plot_1
ggsave("outputs/figures/hist_chap1.png", hist_plot_1, width = 15, height = 15)
```

@@

```{r hist_plot_2, out.width="100%"}
hist_plot_2 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('both', 'chap_2')) %>%  
  ggplot(aes(x=bins, y=n, group=ts, colour=ts)) + 
  geom_density(stat='identity', show.legend=F, aes(fill=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  labs(x = "Flow intensity distribution (log)", 
       y = "") +
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank()) +
  NULL
hist_plot_2
ggsave("outputs/figures/hist_chap2.png", hist_plot_2, width = 15, height = 20)
```

@@

```{r surf_1, message=FALSE}
surf_1 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  NULL
surf_1
ggsave("outputs/figures/surf_chap1.png", surf_1, width = 15, height = 15)
```

@@

surf_radar_1 <- 
  ggradar(surf_radar_data_1, centre.y = -60, legend.position = "right",
          grid.min = -60, grid.max = 5, grid.mid = 0, 
          values.radar = c("-60 %", "0 %", ""), 
          gridline.label.offset	=22, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
surf_radar_1
ggsave("outputs/figures/surf_radar_chap1.png", surf_radar_1, width = 15, height = 10)
```

@@

```{r surf_2, message=FALSE}
surf_2 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  NULL
surf_2
ggsave("outputs/figures/surf_chap2.png", surf_2, width = 15, height = 15)
```

@@

surf_radar_2 <- 
  ggradar(surf_radar_data_2, centre.y = -60, legend.position = "right",
          grid.min = -60, grid.max = 5, grid.mid = 0, 
          values.radar = c("-60 %", "0 %", ""), 
          gridline.label.offset	=22, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
surf_radar_2
ggsave("outputs/figures/surf_radar_chap2.png", surf_radar_2, width = 15, height = 10)
```

```{r eval=FALSE, include=FALSE}
class = 1

@@

aucs <- c()
precs <- c()
for (x in 1:nlayers(the_stack)){
  the_df <- as.data.frame(stack(the_stack[[x]], final)) %>% 
    drop_na() %>% 
    rename(estimate = starts_with("model"), truth = "observation")
  the_df_2 <- the_df %>% 
    mutate(truth = factor(truth, ordered = F)) %>%
    mutate(truth = relevel(.$truth, "1"))
  auc <- the_df_2 %>% 
    roc_auc(truth = truth, estimate) %>% 
    pull(.estimate)
  prec <- the_df_2 %>% 
    average_precision(truth = truth, estimate) %>% 
    pull(.estimate)
  aucs <- c(aucs, auc)
  precs <- c(precs, prec)
}
# plot(stack(the_mean, final))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_knit$set(root.dir = normalizePath(".."))
suppressPackageStartupMessages({
  library(raster)
  library(sf)
  library(tidyverse)
  library(ggplot2)
  library(gganimate)
  library(transformr)
  library(animation)
  library(rasterVis)
  library(ggmap)
  library(gifski)
  library(gtools)
  library(fmsb)
  library(RColorBrewer)
  library(scales)
  library(ggradar)
  library(tidymodels)
  library(patchwork)
})
theme_set(theme_minimal())
theme_update(legend.position = c(0.85, 0.20),
             legend.box = "vertical",
             legend.background = element_blank(),
             legend.box.background = element_rect(colour = "black"),
             panel.border = element_rect(fill = NA),
             legend.title = element_text(size = 15),
             legend.text = element_text(size = 13),
             plot.title = element_text(size=20),
             plot.subtitle = element_text(size=20),
             axis.text.x = element_text(angle=65, vjust=0.6, size =13),
             axis.text.y = element_text(size =13),
             strip.text.x = element_text(size = 13),
             strip.text.y = element_text(13),
             axis.title=element_text(size=18))
```

@@

# Classes
classes <- read_csv("config/rcl_tables/land_use/recode_table.csv")
forest_classes <- read_csv("config/rcl_tables/land_use/recode_table_forest.csv") %>% 
  rename(new_code = "ID", new_class = "Name")

classes_unique <- unique(classes[, c("new_code", "new_class")]) %>% 
  bind_rows(forest_classes)

@@

# Histogram data 
hist_original <- read_csv("outputs/final/final_values_output_original.csv")
hist_true <- read_csv("outputs/final/final_values_output_TRUE.csv") %>% 
  mutate(sce = "TRUE")
histograms <- read_csv("outputs/final/final_values_output.csv") %>% 
  bind_rows(hist_original) %>% 
  bind_rows(hist_true) %>% 
  left_join(results_clean, by="sce")

@@

@@

```{r fig_1_historic, message=FALSE, out.width="100%", fig.cap="Connectivity change for species through time, 1990-2010"}
fig_1_historic <- joined %>% 
  filter(climate == "none") %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 1990)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=source)) +
  scale_color_manual(values=c('#d8b365','#5ab4ac'), 
                     labels = c("Model", "Observation")) +
  geom_smooth(aes(group = sce), method = "glm", se=FALSE) +
  scale_linetype_manual(values = c(1,3,2,5))+
  geom_point(aes(group = sce)) +
  facet_wrap(~species, scales = "fixed") +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Source") +
  NULL
fig_1_historic
ggsave(fig_1_historic,
       filename = "../msc-thesis-mcgill/figures/connectivity_decrease_x5species_historic.png",
       width = 15, height = 15, dpi = 500)
```
#### Chap 1

@@

```{r figure_1_model_1, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100", message=FALSE}
fig_1_static_chap_1 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  #geom_point(aes(group = sce)) +
  scale_linetype_manual(values=c("solid", "twodash")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  #geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
fig_1_static_chap_1
ggsave(fig_1_static_chap_1, 
       filename = "../msc-thesis-mcgill/figures/connectivity_decrease_x5species_chap1.png", 
       width = 15, height = 15)
```

@@

radar_chap1 <-  
  ggradar(radar_data_chap1, centre.y = -20, legend.position = "right",
          grid.min = -20, grid.max = 3, grid.mid = 0, 
          values.radar = c("-20 %", "0 %", ""), 
          gridline.label.offset	=5, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
radar_chap1
ggsave("../msc-thesis-mcgill/figures/radar_ggradar_chap1.png", radar_chap1, width = 15, height = 10)
```

@@

```{r figure_1_model_2, out.width="100%", fig.cap="Connectivity change for species through time, 2010-2100", message=FALSE}
fig_1_static_chap_2 <- joined %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=climate)) +
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  geom_smooth(aes(group = sce, linetype=code_run), alpha=0.5, method="loess") +
  scale_linetype_manual(values=c("solid", "dashed", "longdash", "dotted")) +
  facet_wrap(~species, scales = "fixed") +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  geom_vline(xintercept = 2020, linetype = "dashed", color = "darkGreen", alpha = 0.5) +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow = 2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  theme(legend.position = c(0.85, 0.15))+
  NULL
fig_1_static_chap_2
ggsave(fig_1_static_chap_2, 
       filename = "../msc-thesis-mcgill/figures/connectivity_decrease_x5species_chap2.png", 
       width = 15, height = 15)
```
##### Radar Graph

@@

radar_chap2 <-  
  ggradar(radar_data_chap2, centre.y = -20, legend.position = "right",
          grid.min = -20, grid.max = 3, grid.mid = 0, 
          values.radar = c("-20 %", "0 %", ""), 
          gridline.label.offset	=5, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
radar_chap2
ggsave("../msc-thesis-mcgill/figures/radar_ggradar_chap2.png", radar_chap2, width = 15, height = 10)
```

@@

radar_all <-  
  ggradar(radar_data_all, centre.y = -20, legend.position = "right",
          grid.min = -20, grid.max = 3, grid.mid = 0, 
          values.radar = c("-20 %", "0 %", ""), 
          gridline.label.offset	=5, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
radar_all
ggsave("../msc-thesis-mcgill/figures/radar_ggradar_both.png", radar_all, width = 15, height = 10)
```

@@

```{r figure_2_chap1, eval=FALSE, message=FALSE, warning=FALSE}
# change_1 <- df_final_fordiff_pivoted %>% 
#   filter(chapter %in% c("none", "both", "chap_1")) %>%
#   filter(sce %in% c('sce_39', 'sce_39')) %>% 
#   ggplot(aes(fill=change)) +
#   geom_sf(show.legend=T, lwd = 0)  + 
#   facet_wrap(~sce) + 
#   ggtitle("Connectivity change in %", 
#           subtitle = "2010-2100") +
#   scale_fill_binned(low='#d13e11', high='#fff7bc', 
#                     breaks=c(-50, -40, -30, -20, -10, 0, 10))
# change_1
#ggsave("../msc-thesis-mcgill/figures/connectivit_change_mun_chap1.png", change_1)
```

@@

```{r figure_2_chap2, eval=FALSE, message=FALSE, warning=FALSE}
# change_2 <- df_final_fordiff_pivoted %>% 
#   filter(chapter %in% c("none", "both", "chap_2")) %>%
#   ggplot(aes(fill=change)) +
#   geom_sf(show.legend=T, lwd = 0)  + 
#   facet_wrap(~sce) + 
#   ggtitle("Connectivity change in %", 
#           subtitle = "2010-2100") +
#   scale_fill_binned(low='#d13e11', high='#fff7bc', 
#                     breaks=c(-50, -40, -30, -20, -10, 0, 10))
# change_2
#ggsave("../msc-thesis-mcgill/figures/connectivit_change_mun_chap2.png", change_2)
```

@@

```{r figure_2_all, eval=FALSE, message=FALSE, warning=FALSE}
# change_both <- df_final_fordiff_pivoted %>% 
#   ggplot(aes(fill=change)) +
#   geom_sf(show.legend=T, lwd = 0)  + 
#   facet_wrap(~sce) + 
#   ggtitle("Connectivity change in %", 
#           subtitle = "2010-2100") +
#   scale_fill_binned(low='#d13e11', high='#fff7bc', 
#                     breaks=c(-50, -40, -30, -20, -10, 0, 10))
# change_both
#ggsave("../msc-thesis-mcgill/figures/connectivit_change_mun_both.png", change_both)
```

@@

```{r roc_curves, message=FALSE, warning=FALSE, out.width="100%"}
p1 <- bind_rows(urb, .id = "fold") %>% 
  mutate(Fold = factor(fold, levels = as.character(1:10))) %>% 
  group_by(Fold) %>% 
  roc_curve(.pred, truth = outcome_fact) %>% 
  autoplot(add=T) +
  ggtitle(paste("Urbanisation")) +
  annotate(x = 0.75, y = 0.25, geom="label", size = 3,
           label = as.character(paste("Av AUC = 0.938 +/- 0.002"))) +
  theme(legend.position = "none") +
  NULL

p2 <- bind_rows(agex, .id = "fold") %>% 
  mutate(Fold = factor(fold, levels = as.character(1:10))) %>% 
  group_by(Fold) %>% 
  roc_curve(.pred, truth = outcome_fact) %>% 
  autoplot(add=T) +
  ggtitle(paste("Agricultural Expansion")) +
  annotate(x = 0.75, y = 0.25, geom="label", size = 3,
           label = as.character(paste("Av AUC = 0.929 +/- 0.002"))) +
  NULL

@@

full
ggsave("../msc-thesis-mcgill/figures/double_roc_resample.png", full)
```

@@

```{r hist_plot_1, out.width="100%"}
hist_plot_1 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('both', 'chap_1')) %>%  
  ggplot(aes(x=bins, y=n, group=ts, colour=ts)) + 
  geom_density(stat='identity', show.legend=F, aes(fill=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  labs(x = "Flow intensity distribution (log)", 
       y = "")+
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank()) +
  NULL
hist_plot_1
ggsave("../msc-thesis-mcgill/figures/hist_chap1.png", hist_plot_1, width = 15, height = 15)
```

@@

```{r hist_plot_2, out.width="100%"}
hist_plot_2 <- histograms %>% 
  mutate(ts = as.factor(ts)) %>% 
  filter(chapter %in% c('both', 'chap_2')) %>%  
  ggplot(aes(x=bins, y=n, group=ts, colour=ts)) + 
  geom_density(stat='identity', show.legend=F, aes(fill=factor(ts)), alpha=0.3)+
  facet_grid(code~species) +
  labs(x = "Flow intensity distribution (log)", 
       y = "") +
  theme(strip.text.y = element_text(angle=360, size=10, hjust = 0), 
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(), 
        axis.text.y.left = element_blank(),
        axis.ticks.y.left = element_blank()) +
  NULL
hist_plot_2
ggsave("../msc-thesis-mcgill/figures/hist_chap2.png", hist_plot_2, width = 15, height = 20)
```

@@

```{r surf_1, message=FALSE}
surf_1 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_1")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=1, override.aes = list(colour = 'black'))) +
  NULL
surf_1
ggsave("../msc-thesis-mcgill/figures/surf_chap1.png", surf_1, width = 15, height = 15)
```

@@

surf_radar_1 <- 
  ggradar(surf_radar_data_1, centre.y = -60, legend.position = "right",
          grid.min = -60, grid.max = 5, grid.mid = 0, 
          values.radar = c("-60 %", "0 %", ""), 
          gridline.label.offset	=22, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
surf_radar_1
ggsave("../msc-thesis-mcgill/figures/surf_radar_chap1.png", surf_radar_1, width = 15, height = 10)
```

@@

```{r surf_2, message=FALSE}
surf_2 <- surf %>% 
  mutate(scenario = as.factor(scenario)) %>% 
  filter(climate != "none", chapter %in% c("none", "both", "chap_2")) %>% 
  filter(climate != "none") %>% 
  group_by(scenario, species, iter) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 2010)$kp_nb, 
                       the_diff = ((kp_nb-baseline)/baseline)*100 )) %>% ungroup %>% 
  ggplot(aes(x = timestep, y = the_diff, color=climate)) +
  geom_smooth(aes(group = scenario, linetype=code_run), alpha=0.2, method="loess")+
  #geom_point(aes(group=scenario), alpha= 0.05, size = 0.5)+
  facet_wrap(~species, scales = "fixed")+
  scale_color_manual(values=c('#ffe300', '#ff7a14', "#b31400"), 
                     labels = c("Historic", "Baseline", "RCP 8.5")) +
  labs(y = "Change in nb of Keypoints detected (%)",
       x = "Year",
       col = "Climate",
       linetype = "Run") +
  guides(col = guide_legend(ncol = 2, nrow=2), 
         linetype = guide_legend(nrow=2, ncol=2, 
                                 override.aes = list(colour = 'black'))) +
  NULL
surf_2
ggsave("../msc-thesis-mcgill/figures/surf_chap2.png", surf_2, width = 15, height = 15)
```

@@

surf_radar_2 <- 
  ggradar(surf_radar_data_2, centre.y = -60, legend.position = "right",
          grid.min = -60, grid.max = 5, grid.mid = 0, 
          values.radar = c("-60 %", "0 %", ""), 
          gridline.label.offset	=22, legend.text.size= 12,
          group.line.width =0.8,
          background.circle.colour	= "#ffffff", group.point.size	= 2, 
          axis.label.size=5)
surf_radar_2
ggsave("../msc-thesis-mcgill/figures/surf_radar_chap2.png", surf_radar_2, width = 15, height = 10)
```

### Maps

```{r eval=FALSE, include=FALSE}
class = 2

@@

aucs <- c()
precs <- c()
for (x in 1:nlayers(the_stack)){
  the_df <- as.data.frame(stack(the_stack[[x]], final)) %>% 
    drop_na() %>% 
    rename(estimate = starts_with("model"), truth = "observation")
  the_df_2 <- the_df %>% 
    mutate(truth = factor(truth, ordered = F)) %>%
    mutate(truth = relevel(.$truth, "1"))
  auc <- the_df_2 %>% 
    roc_auc(truth = truth, estimate) %>% 
    pull(.estimate)
  prec <- the_df_2 %>% 
    average_precision(truth = truth, estimate) %>% 
    pull(.estimate)
  aucs <- c(aucs, auc)
  precs <- c(precs, prec)
}
mean(aucs);sd(aucs)
mean(precs);sd(precs)
# plot(stack(the_mean, final))
```

### Original hist
